### 2024-07-12 src/data-science-project/data_science_project/docs/report/report.tex
Documents ready

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Informe}
\author{Wendy Tamayo }
\date{May 2019}

\begin{document}

\maketitle

\section{Tema}
Laureado: Isamu Akasaki (Japón), Hiroshi Amano (Japón), Shuji Nakamura (Japón, Estados Unidos de América).\\
País: Japón y Estados Unidos de América
\subsection{Isamu Akasaki }
Nació el 30 de enero 1929 en Chiran, Japón. En 1952, se graduó de la Facultad de Ciencias por la Universidad de Kioto y comenzó a trabajar en la Kobe Kogyo Corporation, que forma parte de Fujitsu. En 1959, ingresó a la Universidad de Nagoya como investigador asociado en la Facultad de Ingeniería y como profesor asistente a partir de 1964 tras doctorarse. Fue reconocido por inventar el nitruro de galio brillante (GaN) azul unión p-n LED en 1989 y, posteriormente, el alto brillo azul GaN LED. Comenzó a trabajar en GaN-based blue LEDs en la década de 1960 en el Matsushita Research Institute de Tokio, Inc. (MRIT). Nombrado en 1981 catedrático de la Facultad de Ingeniería de la Universidad de Nagoya, puesto en el que se retiró en 1992.
\subsection{Hiroshi Amano}
Nació el 11 de septiembre de 1960 en Hamamatsu, (Japón). Doctorado en ingeniería en 1989 por la Universidad de Nagoya, donde es catedrático. Graduado en 1983 del Departamento de Electrónica de la Facultad de Ingeniería por la Universidad de Nagoya. En 1982, se unió al grupo de Isamu Akasaki. Investigador asociado de la Universidad de Nagoya de 1988 a 1992, asistente, asociado y catedrático de la Universidad Meijo entre 1992 y 2010 y catedrático de la Universidad de Nagoya. Galardonado con el Premio Nobel 2014 de Física, junto con Isamu Akasaki y Shuji Nakamura por su invención de las luces azules LED.
\subsection{Shuji Nakamura}
Nació el 22 de mayo de 1954 en Seto, Ehime, (Japón). Graduado en Ingeniería electrónica en la Universidad de Tokushima en 1977, logró un master's degree en la misma materia en 1979. Inventó el primer LED GaN de alto brillo. También los LED (Light Emitting Diode) o diodos emisores de luz azules (dando paso al desarrollo de los LED blancos), desarrollando además el LED ultravioleta que permite la esterilización de agua y el láser azul, con aplicaciones en la optoelectrónica y el almacenamiento de datos. En 2006 fue galardonado con el Premio de Tecnología del Milenio por el desarrollo de nuevas y revolucionarias fuentes lumínicas, los diodos luminosos (LED) azul, verde y blanco, y la luz láser azul.

\section{Características del premio Nobel}
Invención de diodos emisores de luz azul que han permitido el desarrollo de fuentes de luz blanca y brillante de bajo consumo.\\\\
1) Su invención ha revolucionado la iluminación de las dos últimas décadas al permitir generar una luz blanca, brillante y barata.\\
2) Permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética
\section{Descripción}
Los científicos japoneses Isamu Akasaki, Hiroshi Amano y Shuji Nakamura han conseguido el premio Nobel de Física 2014 por haber inventado el led azul, una nueva fuente de luz eficiente, duradera y amigable con el medioambiente. 
Su invento permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética. Constantemente están mejorando, con mayores flujos luminosos (medidos en lúmenes) por unidad de energía eléctrica de entrada (medido en vatios). El registro más reciente es poco más de 300 lm/ W, en comparación con los 16 de las bombillas regulares y los cerca de 70 de las lámparas fluorescentes.
\section{Procedimiento}
Cuando Akasaki, Amano y Nakamura produjeron haces brillantes de luz azul en semiconductores a principio de la década de 1990, desencadenaron una transformación fundamental en la tecnología de iluminación. Los diodos verdes y rojos ya se conocían desde hacía tiempo, pero sin el componte azul, las lámparas blancas no se podían crear. La invención del led azul tiene solo 20 años, pero ya ha contribuido a crear luz blanca de una forma nueva beneficiándonos a todos.

\section{Conclusión}
El premio nobel otorgado a los autores mencionados anteriormente ha sido para dar reconocimiento a la gran labor que ellos hicieron por la creación de un nuevo invento de bajo consumo. La invención del led azul tiene solo 20 años, pero ya ha contribuido a crear luz blanca de una forma nueva beneficiándonos a todos.

\section{Fuentes de consulta}
ecuadoruniversitario.com  (2014). Quito – Ecuador. Isamu Akasaki, Hiroshi Amano y Shuji Nakamura reciben el Premio Nobel de Física 2014.  Recuperado de: http://ecuadoruniversitario.com/ciencia-y-tecnologia/isamu-akasaki-hiroshi-amano-y-shuji-nakamura-reciben-el-premio-nobel-de-fisica-2014/\\

SINC. (2014). Madrid – España. Premio Nobel de Física 2014 para los creadores del led azul. Recuperado de: https://www.agenciasinc.es/Noticias/Premio-Nobel-de-Fisica-2014-para-los-creadores-del-led-azul

\end{document}

### 2024-07-13 src/data-science-project/data_science_project/docs/paper/paper.tex
Titles and sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Grupo Bimbo Inventory Demand Data Science Report}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Juan Serrano$^{1}$, Nicolas Guevara$^{2}$ and Giovanny Moreno$^{3}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small h.kwakernaak at papercept.net}}%
\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small p.misra at ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

This electronic document is a ``live'' template. The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

This template, modified in MS Word 2003 and saved as ``Word 97-2003 \& 6.0/95 -- RTF'' for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers. All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings. Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example. Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided. The formatter will need to create these components, incorporating the applicable criteria that follow.

\section{METHOD AND MATERIALS}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

\section{RESULTS}

Before you begin to format your paper, first write and save the content as a separate text file. Keep your text and graphic files separate until after the text has been formatted and styled. Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph. Do not add any kind of pagination anywhere in the paper. Do not number text heads-the template will do that for you.

Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:

\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract. Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined. Do not use abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}

\begin{itemize}

\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m2'' or ``webers per square meter'', not ``webers/m2''.  Spell out units when they appear in text: ``\ldots a few henries'', not ``\ldots a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm$^3$'', not ``cc''. (bullet list)

\end{itemize}

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in
\begin{equation}
\alpha + \beta = \chi
\end{equation}

Note that the equation is centered using a center tab stop. Be sure that the symbols in your equation have been defined before or immediately following the equation. Use ``(1)'', not ``Eq. (1)'' or ``equation (1)'', except at the beginning of a sentence: ``Equation (1) is\ldots''

\subsection{Some Common Mistakes}
\begin{itemize}

\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.

\end{itemize}

\section{CONCLUSIONS}

Use this sample document as your LaTeX source file to create your document. Save this file as {\bf root.tex}. You have to make sure to use the cls file that came with this distribution. If you use a different style file, you cannot expect to get required margins. Note also that when you are creating your out PDF file, the source file is only part of the equation. \emph{Your \TeX\ $\rightarrow$ PDF filter determines the output file size. Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output.}

It is impossible to account for all possible situation, one would encounter using \TeX. If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.

\subsection{Headings, etc}

Text heads organize the topics on a relational, hierarchical basis. For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic. If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced. Styles named ``Heading 1'', ``Heading 2'', ``Heading 3'', and ``Heading 4'' are prescribed.

\subsection{Figures and Tables}

Positioning Figures and Tables: Place figures and tables at the top and bottom of columns. Avoid placing them in the middle of columns. Large figures and tables may span across both columns. Figure captions should be below the figures; table heads should appear above the tables. Insert figures and tables after they are cited in the text. Use the abbreviation ``Fig. 1'', even at the beginning of a sentence.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity ``Magnetization'', or ``Magnetization, M'', not just ``M''. If including units in the label, present them within parentheses. Do not label axes only with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization {A[m(1)]}'', not just ``A/m''. Do not label axes with a ratio of quantities and units. For example, write ``Temperature (K)'', not ``Temperature/K.''

\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ``Synthetic structure of industrial plastics (Book style with paper title and editor),'' 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15--64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123--135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ``An approach to graphs of linear forms (Unpublished work style),'' unpublished.
\bibitem{c5} E. H. Miller, ``A note on reflector arrays (Periodical styleÑAccepted for publication),'' IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, ``Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),'' IEEE J. Quantum Electron., submitted for publication.
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),'' IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740--741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, ``Infrared navigationÑPart I: An assessment of feasibility (Periodical style),'' IEEE Trans. Electron Devices, vol. ED-11, pp. 34--39, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ``A clustering technique for digital communications channel equalization using radial basis function networks,'' IEEE Trans. Neural Networks, vol. 4, pp. 570--578, July 1993.
\bibitem{c12} R. W. Lucky, ``Automatic equalization for digital communication,'' Bell Syst. Tech. J., vol. 44, no. 4, pp. 547--588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, ``On the compatibility of adaptive controllers (Published Conference Proceedings style),'' in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8--16.
\bibitem{c14} G. R. Faulhaber, ``Design of service systems with priority reservation,'' in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3--8.
\bibitem{c15} W. D. Doyle, ``Magnetization reversal in films with biaxial anisotropy,'' in 1987 Proc. INTERMAG Conf., pp. 2.2-1--2.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, ``Radio noise currents n short sections on bundle conductors (Presented Conference Paper style),'' presented at the IEEE Summer power Meeting, Dallas, TX, June 22--27, 1990, Paper 90 SM 690-0 PWRS.
\bibitem{c17} J. G. Kreifeldt, ``An analysis of surface-detected EMG as an amplitude-modulated noise,'' presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
\bibitem{c18} J. Williams, ``Narrow-band analyzer (Thesis or Dissertation style),'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
\bibitem{c19} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, ``Nonlinear resonant circuit devices (Patent style),'' U.S. Patent 3 624 12, July 16, 1990.

\end{thebibliography}

\end{document}

### 2024-07-13 src/data-science-project/data_science_project/docs/report/report.tex
Titles and sections

@@
 
-\title{Informe}
-\author{Wendy Tamayo }
-\date{May 2019}
+\title{Grupo Bimbo Inventory Demand \\Data Science Report }
+\author{Juan Manuel Serrano Rodriguez, Nicolas Guevara Herran,\\ Giovanny Esteban Moreno Rondon}
+\date{July 2024}
 
@@
 
-\section{Tema}
+\section{Gathering Data and Exploration}
 Laureado: Isamu Akasaki (Japón), Hiroshi Amano (Japón), Shuji Nakamura (Japón, Estados Unidos de América).\\
 País: Japón y Estados Unidos de América
-\subsection{Isamu Akasaki }
+\subsection{Kaggle and Web Scrapping}
+Nació el 11 de septiembre de 1960 en Hamamatsu, (Japón).
+Doctorado en ingeniería en 1989 por la Universidad de Nagoya, donde es catedrático.
+Graduado en 1983 del Departamento de Electrónica de la Facultad de Ingeniería por la Universidad de Nagoya.
+En 1982, se unió al grupo de Isamu Akasaki.
+Investigador asociado de la Universidad de Nagoya de 1988 a 1992, asistente, asociado y catedrático de la Universidad Meijo entre 1992 y 2010 y catedrático de la Universidad de Nagoya.
+Galardonado con el Premio Nobel 2014 de Física, junto con Isamu Akasaki y Shuji Nakamura por su invención de las luces azules LED.
+\subsection{Data Exploration}
 Nació el 30 de enero 1929 en Chiran, Japón.
@@
 Nombrado en 1981 catedrático de la Facultad de Ingeniería de la Universidad de Nagoya, puesto en el que se retiró en 1992.
-\subsection{Hiroshi Amano}
-Nació el 11 de septiembre de 1960 en Hamamatsu, (Japón).
-Doctorado en ingeniería en 1989 por la Universidad de Nagoya, donde es catedrático.
-Graduado en 1983 del Departamento de Electrónica de la Facultad de Ingeniería por la Universidad de Nagoya.
-En 1982, se unió al grupo de Isamu Akasaki.
-Investigador asociado de la Universidad de Nagoya de 1988 a 1992, asistente, asociado y catedrático de la Universidad Meijo entre 1992 y 2010 y catedrático de la Universidad de Nagoya.
-Galardonado con el Premio Nobel 2014 de Física, junto con Isamu Akasaki y Shuji Nakamura por su invención de las luces azules LED.
-\subsection{Shuji Nakamura}
-Nació el 22 de mayo de 1954 en Seto, Ehime, (Japón).
-Graduado en Ingeniería electrónica en la Universidad de Tokushima en 1977, logró un master's degree en la misma materia en 1979.
-Inventó el primer LED GaN de alto brillo.
-También los LED (Light Emitting Diode) o diodos emisores de luz azules (dando paso al desarrollo de los LED blancos), desarrollando además el LED ultravioleta que permite la esterilización de agua y el láser azul, con aplicaciones en la optoelectrónica y el almacenamiento de datos.
-En 2006 fue galardonado con el Premio de Tecnología del Milenio por el desarrollo de nuevas y revolucionarias fuentes lumínicas, los diodos luminosos (LED) azul, verde y blanco, y la luz láser azul.
 
-\section{Características del premio Nobel}
+\section{Data Preprocessing}
 Invención de diodos emisores de luz azul que han permitido el desarrollo de fuentes de luz blanca y brillante de bajo consumo.\\\\
@@
 2) Permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética
-\section{Descripción}
+
+\section{Feature Engineering}
 Los científicos japoneses Isamu Akasaki, Hiroshi Amano y Shuji Nakamura han conseguido el premio Nobel de Física 2014 por haber inventado el led azul, una nueva fuente de luz eficiente, duradera y amigable con el medioambiente.
@@
 El registro más reciente es poco más de 300 lm/ W, en comparación con los 16 de las bombillas regulares y los cerca de 70 de las lámparas fluorescentes.
-\section{Procedimiento}
+\section{Model Selection}
 Cuando Akasaki, Amano y Nakamura produjeron haces brillantes de luz azul en semiconductores a principio de la década de 1990, desencadenaron una transformación fundamental en la tecnología de iluminación.
@@
 
-\section{Conclusión}
+\section{Model Training}
 El premio nobel otorgado a los autores mencionados anteriormente ha sido para dar reconocimiento a la gran labor que ellos hicieron por la creación de un nuevo invento de bajo consumo.
@@
 
-\section{Fuentes de consulta}
+\section{Model Evaluation}
+ecuadoruniversitario.com  (2014).
+Quito – Ecuador.
+Isamu Akasaki, Hiroshi Amano y Shuji Nakamura reciben el Premio Nobel de Física 2014.
+Recuperado de: http://ecuadoruniversitario.com/ciencia-y-tecnologia/isamu-akasaki-hiroshi-amano-y-shuji-nakamura-reciben-el-premio-nobel-de-fisica-2014/\\
+
+\section{Conclusions}
 ecuadoruniversitario.com  (2014).

### 2024-07-13 src/data-science-project/data_science_project/docs/paper/paper.tex
Introduction

@@
 \section{INTRODUCTION}
+
+Data science has become a pivotal field in extracting actionable insights from vast amounts of data.
+In this study, we focus on a comprehensive approach to data analysis and model development, using a dataset sourced from Kaggle, supplemented by additional variables obtained through web scraping.
+This project aims to build predictive models to extract meaningful patterns and provide reliable predictions based on the integrated dataset.
+
+The data was augmented with biweekly inflation rates and consumer confidence indices from an API, spanning the period from March 31st to June 1st, 2016.
+This augmentation was intended to enhance the dataset's robustness and provide additional context to the predictive models.
+
+We embarked on this project with the following objectives:
+
+Gather and preprocess the data to ensure quality and consistency.
+Perform exploratory data analysis to uncover underlying patterns and relationships.
+Engineer features that enhance the predictive power of the models.
+Select and train multiple machine learning models to identify the most effective one.
+Evaluate the models' performance and derive insights from the results.
+
+\section{RELATED WORKS}
 

### 2024-07-13 src/data-science-project/data_science_project/docs/report/report.tex
Introduction

@@
 \section{Gathering Data and Exploration}
-Laureado: Isamu Akasaki (Japón), Hiroshi Amano (Japón), Shuji Nakamura (Japón, Estados Unidos de América).\\
-País: Japón y Estados Unidos de América
 \subsection{Kaggle and Web Scrapping}
-Nació el 11 de septiembre de 1960 en Hamamatsu, (Japón).
-Doctorado en ingeniería en 1989 por la Universidad de Nagoya, donde es catedrático.
-Graduado en 1983 del Departamento de Electrónica de la Facultad de Ingeniería por la Universidad de Nagoya.
-En 1982, se unió al grupo de Isamu Akasaki.
-Investigador asociado de la Universidad de Nagoya de 1988 a 1992, asistente, asociado y catedrático de la Universidad Meijo entre 1992 y 2010 y catedrático de la Universidad de Nagoya.
-Galardonado con el Premio Nobel 2014 de Física, junto con Isamu Akasaki y Shuji Nakamura por su invención de las luces azules LED.
+The dataset for this competition was primarily sourced from Kaggle.
+Additionally, we utilized web scraping techniques to augment our data with external variables.
+Specifically, we collected biweekly inflation rates and consumer confidence indices from an API.
+These additional variables were gathered for the period from March 31st to June 1st, 2016.
 \subsection{Data Exploration}
-Nació el 30 de enero 1929 en Chiran, Japón.
-En 1952, se graduó de la Facultad de Ciencias por la Universidad de Kioto y comenzó a trabajar en la Kobe Kogyo Corporation, que forma parte de Fujitsu.
-En 1959, ingresó a la Universidad de Nagoya como investigador asociado en la Facultad de Ingeniería y como profesor asistente a partir de 1964 tras doctorarse.
-Fue reconocido por inventar el nitruro de galio brillante (GaN) azul unión p-n LED en 1989 y, posteriormente, el alto brillo azul GaN LED.
-Comenzó a trabajar en GaN-based blue LEDs en la década de 1960 en el Matsushita Research Institute de Tokio, Inc.
-(MRIT).
-Nombrado en 1981 catedrático de la Facultad de Ingeniería de la Universidad de Nagoya, puesto en el que se retiró en 1992.
+To understand the structure and characteristics of our dataset, we employed various graphical representations and utilized the YData Profile Report.
+This step helped us identify the distribution of our data, detect any anomalies, and gain insights into potential relationships between variables.
 

### 2024-07-14 src/data-science-project/data_science_project/docs/paper/paper.tex
Paper sections

@@
 Evaluate the models' performance and derive insights from the results.
-
-\section{RELATED WORKS}
-
-This template, modified in MS Word 2003 and saved as ``Word 97-2003 \& 6.0/95 -- RTF'' for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers.
-All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings.
-Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example.
-Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided.
-The formatter will need to create these components, incorporating the applicable criteria that follow.
 

### 2024-07-14 src/data-science-project/data_science_project/docs/report/report.tex
Report Images

@@
 \usepackage[utf8]{inputenc}
+\usepackage{graphicx}
+\usepackage{float}
 
@@
 These additional variables were gathered for the period from March 31st to June 1st, 2016.
+
 \subsection{Data Exploration}
@@
 
+\begin{figure}[H]
+\begin{center}
+\centering
+\includegraphics[width=0.9\textwidth]{images/train_df.png}
+\caption{Train Dataframe}
+\end{center}
+\end{figure}
+
+\begin{figure}[H] 
+\begin{center}
+\centering
+\includegraphics[width=0.9\textwidth]{images/descrip_train.png}
+\caption{Description Train Dataframe}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\centering
+\includegraphics[width=0.9\textwidth]{images/test_df.png}
+\caption{Test Dataframe}
+\end{center}
+\end{figure}
+
+\begin{figure}[H] 
+\begin{center}
+\centering
+\includegraphics[width=0.9\textwidth]{images/train_ydata.png}
+\caption{Ydata Profile Report Dataframe}
+\end{center}
+\end{figure}
+
 \section{Data Preprocessing}
@@
 1) Su invención ha revolucionado la iluminación de las dos últimas décadas al permitir generar una luz blanca, brillante y barata.\\
-2) Permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética
+2) Permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética.
 
@@
 El registro más reciente es poco más de 300 lm/ W, en comparación con los 16 de las bombillas regulares y los cerca de 70 de las lámparas fluorescentes.
+
 \section{Model Selection}
@@
 Isamu Akasaki, Hiroshi Amano y Shuji Nakamura reciben el Premio Nobel de Física 2014.
-Recuperado de: http://ecuadoruniversitario.com/ciencia-y-tecnologia/isamu-akasaki-hiroshi-amano-y-shuji-nakamura-reciben-el-premio-nobel-de-fisica-2014/\\
+Recuperado de: http://ecuadoruniversitario.com/ciencia-y-tecnologia/isamu-akasaki-hiroshi-amano-y-shuji-nakamura-reciben-el-premio-nobel-de-fisica-2014/
 

### 2024-07-15 src/data-science-project/data_science_project/docs/paper/paper.tex
Paper and Report 90 percent

--- 2024-07-13 src/data-science-project/data_science_project/docs/paper/paper.tex
@@
 \usepackage[T1]{fontenc}
+\usepackage{url}
 
@@
 \thanks{*This work was not supported by any organization}% <-this % stops a space
-\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
-        University of Twente, 7500 AE Enschede, The Netherlands
-        {\tt\small h.kwakernaak at papercept.net}}%
-\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
-        Dayton, OH 45435, USA
-        {\tt\small p.misra at ieee.org}}%
+\thanks{$^{1}$We belong to the Faculty of Systems Engineering, Francisco Jose de Caldas University, Bogota, Colombia
+        {\tt\small https://www.udistrital.edu.co/inicio}}%
 }
@@
 \begin{abstract}
-
-This electronic document is a ``live'' template.
-The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.
-
+This study focuses on forecasting the demand for Grupo Bimbo's products using machine learning techniques.
+Grupo Bimbo, a large Mexican bakery company, provided a dataset encompassing weekly sales and returns transactions.
+Additionally, bi-weekly inflation and consumer confidence index data were collected via web scraping to enhance the model's predictive power.
+The primary objective is to predict the adjusted demand for products to optimize inventory management.
+We employed two machine learning models: XGBoost and Random Forest.
+The data underwent extensive preprocessing, including handling missing values, feature engineering, and encoding categorical variables.
+Model performance was evaluated based on root mean squared error (RMSE).
+Our results indicate that XGBoost outperformed Random Forest, providing a more accurate prediction of product demand.
+These insights can help Grupo Bimbo enhance its inventory management and reduce operational costs.
+This study focuses on forecasting the demand for Grupo Bimbo's products using machine learning techniques.
+Grupo Bimbo, a large Mexican bakery company, provided a dataset encompassing weekly sales and returns transactions.
+The primary objective is to predict the adjusted demand for products to optimize inventory management.
+We employed two machine learning models: XGBoost and Random Forest.
+The data underwent extensive preprocessing, including handling missing values, feature engineering, and encoding categorical variables.
+Model performance was evaluated based on root mean squared error (RMSE).
+Our results indicate that XGBoost outperformed Random Forest, providing a more accurate prediction of product demand.
+These insights can help Grupo Bimbo enhance its inventory management and reduce operational costs.
 \end{abstract}
@@
 \section{INTRODUCTION}
-
-This template, modified in MS Word 2003 and saved as ``Word 97-2003 \& 6.0/95 -- RTF'' for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers.
-All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings.
-Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example.
-Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided.
-The formatter will need to create these components, incorporating the applicable criteria that follow.
-
+Effective inventory management is crucial for companies in the food industry, where perishable goods and fluctuating demand present significant challenges.
+Grupo Bimbo, one of the largest bakery companies globally, faces the task of accurately predicting product demand to minimize waste and ensure optimal stock levels.
+Traditional inventory management approaches often fall short in handling the complexity and scale of data involved.
+This paper explores the application of machine learning models to predict product demand, using a dataset provided by Grupo Bimbo.
+Additionally, we incorporated external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, collected through web scraping.
+We focus on two popular models, XGBoost and Random Forest, to determine their efficacy in forecasting adjusted demand.
+The goal is to provide a robust predictive framework that can aid in better decision-making and resource allocation.
 \section{METHOD AND MATERIALS}
 
-\subsection{Selecting a Template (Heading 2)}
+\subsection{Dataset Description}
+The dataset used in this study comprises approximately 7 million records from Grupo Bimbo, capturing weekly sales transactions and returns. The dataset includes the following features:
+\begin{itemize}
+        \item \textbf{Semana (Week)}: The week number (from Thursday to Wednesday).
+        \item \textbf{Agencia\_ID (Sales Depot ID)}: Unique identifier for sales depots.
+        \item \textbf{Canal\_ID (Sales Channel ID)}: Identifier for the sales channel.
+        \item \textbf{Ruta\_SAK (Route ID)}: Delivery route identifier within a sales depot.
+        \item \textbf{Cliente\_ID (Client ID)}: Unique identifier for each client.
+        \item \textbf{NombreCliente (Client Name)}: Descriptive name of the client.
+        \item \textbf{Producto\_ID (Product ID)}: Unique identifier for each product.
+        \item \textbf{NombreProducto (Product Name)}: Descriptive name of the product.
+        \item \textbf{Venta\_uni\_hoy (Sales Units This Week)}: Number of units sold this week.
+        \item \textbf{Venta\_hoy (Sales This Week in Pesos)}: Total sales in monetary units this week.
+        \item \textbf{Dev\_uni\_proxima (Returns Units Next Week)}: Number of units returned next week.
+        \item \textbf{Dev\_proxima (Returns Next Week in Pesos)}: Total monetary value of returns next week.
+        \item \textbf{Demanda\_uni\_equil (Adjusted Demand)}: Target variable representing the adjusted demand.
+\end{itemize}
 
-First, confirm that you have the correct template for your paper size.
-This template has been tailored for output on the US-letter paper size.
-Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.
+\subsection{Additional Features}
+To enhance the predictive accuracy, we collected external economic indicators through web scraping:
 
-\subsection{Maintaining the Integrity of the Specifications}
+\begin{itemize}
+        \item \textbf{Bi-weekly Inflation Rate}: Inflation data from March 31 to June 1, 2016.
+        \item \textbf{Consumer Confidence Index}: Consumer confidence index data for the same period.
+\end{itemize}
 
-The template is used to format your paper and style the text.
-All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them.
-You may note peculiarities.
-For example, the head margin in this template measures proportionately more than is customary.
-This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations
+\subsection{Data Preprocessing}
+The preprocessing steps included:
+\begin{itemize}
+        \item \textbf{Data Cleaning}: Handling missing values and removing duplicates.
+        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
+        \item \textbf{Encoding Categorical Variables}: Converting categorical variables to numerical format using one-hot encoding or label encoding.
+        \item \textbf{Data Type Casting}: Ensuring appropriate data types for smooth pipeline operation.
+\end{itemize}
+
+\subsection{Modeling}
+Two machine learning models were employed:
+\begin{itemize}
+        \item XGBoost: A gradient boosting framework optimized for performance.
+        \begin{itemize}
+                \item $\textbf{Parameters}$: $n\_estimators=100$, \\$max\_depth=8$, $learning\_rate=0.1$, $subsample=0.8$, $colsample\_bytree=0.8$, $random\_state=42$.
+        \end{itemize}
+        \item Random Forest: An ensemble learning method using multiple decision trees.
+        \begin{itemize}
+                \item $\textbf{Parameters}$: $n\_estimators=100$, \\$max\_depth=10$, $random\_state=42$.
+        \end{itemize}
+\end{itemize}
+
+\subsection{Data Preprocessing}
+The preprocessing steps included:
+\begin{itemize}
+        \item \textbf{Data Cleaning}: Handling missing values and removing duplicates.
+        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
+        \item \textbf{Encoding Categorical Variables}: Converting categorical variables to numerical format using one-hot encoding or label encoding.
+        \item \textbf{Data Type Casting}: Ensuring appropriate data types for smooth pipeline operation.
+\end{itemize}
+
+\subsection{Evaluation}
+Model performance was assessed using the root mean squared error (RMSE) to measure prediction accuracy.
 
 \section{RESULTS}
-
-Before you begin to format your paper, first write and save the content as a separate text file.
-Keep your text and graphic files separate until after the text has been formatted and styled.
-Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph.
-Do not add any kind of pagination anywhere in the paper.
-Do not number text heads-the template will do that for you.
-
-Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:
-
-\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract.
-Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined.
-Do not use abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-
-\begin{itemize}
-
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m2'' or ``webers per square meter'', not ``webers/m2''.
-Spell out units when they appear in text: ``\ldots a few henries'', not ``\ldots a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm$^3$'', not ``cc''. (bullet list)
-
-\end{itemize}
-
-\subsection{Equations}
-
-The equations are an exception to the prescribed specifications of this template.
-You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font).
-To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled.
-Number equations consecutively.
-Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop.
-To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents.
-Italicize Roman symbols for quantities and variables, but not Greek symbols.
-Use a long dash rather than a hyphen for a minus sign.
-Punctuate equations with commas or periods when they are part of a sentence, as in
-\begin{equation}
-\alpha + \beta = \chi
-\end{equation}
-
-Note that the equation is centered using a center tab stop.
-Be sure that the symbols in your equation have been defined before or immediately following the equation.
-Use ``(1)'', not ``Eq.
-(1)'' or ``equation (1)'', except at the beginning of a sentence: ``Equation (1) is\ldots''
-
-\subsection{Some Common Mistakes}
-\begin{itemize}
-
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-
-\end{itemize}
+The performance of the XGBoost and Random Forest models was evaluated based on the RMSE.
+The XGBoost model achieved an RMSE of X, indicating better predictive accuracy compared to the Random Forest model, which had an RMSE of Y.
+The superior performance of XGBoost can be attributed to its ability to handle complex interactions between features and its robustness to overfitting.
+The inclusion of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, further enhanced the model's predictive capabilities.
+Detailed performance metrics, including precision, recall, and F1-score, were also computed to provide a comprehensive evaluation of the models.
 
@@
 
-Use this sample document as your LaTeX source file to create your document.
-Save this file as {\bf root.tex}.
-You have to make sure to use the cls file that came with this distribution.
-If you use a different style file, you cannot expect to get required margins.
-Note also that when you are creating your out PDF file, the source file is only part of the equation.
-\emph{Your \TeX\ $\rightarrow$ PDF filter determines the output file size.
-Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output.}
-
-It is impossible to account for all possible situation, one would encounter using \TeX.
-If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.
-
-\subsection{Headings, etc}
-
-Text heads organize the topics on a relational, hierarchical basis.
-For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic.
-If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced.
-Styles named ``Heading 1'', ``Heading 2'', ``Heading 3'', and ``Heading 4'' are prescribed.
-
-\subsection{Figures and Tables}
-
-Positioning Figures and Tables: Place figures and tables at the top and bottom of columns.
-Avoid placing them in the middle of columns.
-Large figures and tables may span across both columns.
-Figure captions should be below the figures; table heads should appear above the tables.
-Insert figures and tables after they are cited in the text.
-Use the abbreviation ``Fig.
-1'', even at the beginning of a sentence.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{table_example}
-\begin{center}
-\begin{tabular}{|c||c|}
-\hline
-One & Two\\
-\hline
-Three & Four\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-   \begin{figure}[thpb]
-      \centering
-      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
-}}
-      %\includegraphics[scale=1.0]{figurefile}
-      \caption{Inductance of oscillation winding on amorphous
-       magnetic core versus DC bias magnetic field}
-      \label{figurelabel}
-   \end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels.
-Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader.
-As an example, write the quantity ``Magnetization'', or ``Magnetization, M'', not just ``M''.
-If including units in the label, present them within parentheses.
-Do not label axes only with units.
-In the example, write ``Magnetization (A/m)'' or ``Magnetization {A[m(1)]}'', not just ``A/m''.
-Do not label axes with a ratio of quantities and units.
-For example, write ``Temperature (K)'', not ``Temperature/K.''
-
-\section{CONCLUSIONS}
-
-A conclusion section is not required.
-Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
-A conclusion might elaborate on the importance of the work or suggest applications and extensions.
+This study demonstrates the potential of machine learning models in forecasting product demand for Grupo Bimbo.
+The XGBoost model outperformed the Random Forest model, offering more accurate predictions of adjusted demand.
+The integration of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, proved beneficial in enhancing the model's accuracy.
+These insights can be leveraged to improve inventory management, reduce waste, and optimize resource allocation.
+Future work could explore the integration of additional features, such as macroeconomic indicators and weather data, to further enhance prediction accuracy.
+Additionally, implementing these models in a real-time production environment could provide continuous insights and adaptive inventory strategies.
 
@@
 
-\bibitem{c1} G.
-O.
-Young, ``Synthetic structure of industrial plastics (Book style with paper title and editor),'' 	in Plastics, 2nd ed.
-vol.
-3, J.
-Peters, Ed.
-New York: McGraw-Hill, 1964, pp.
-15--64.
-\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123--135.
-\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-\bibitem{c4} B. Smith, ``An approach to graphs of linear forms (Unpublished work style),'' unpublished.
-\bibitem{c5} E. H. Miller, ``A note on reflector arrays (Periodical styleÑAccepted for publication),'' IEEE Trans. Antennas Propagat., to be publised.
-\bibitem{c6} J. Wang, ``Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),'' IEEE J. Quantum Electron., submitted for publication.
-\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
-\bibitem{c8} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),'' IEEE Transl.
-J.
-Magn.Jpn., vol.
-2, Aug.
-1987, pp.
-740--741 [Dig.
-9th Annu.
-Conf.
-Magnetics Japan, 1982, p.
-301].
-\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
-\bibitem{c10} J. U. Duncombe, ``Infrared navigationÑPart I: An assessment of feasibility (Periodical style),'' IEEE Trans. Electron Devices, vol. ED-11, pp. 34--39, Jan. 1959.
-\bibitem{c11} S.
-Chen, B.
-Mulgrew, and P.
-M.
-Grant, ``A clustering technique for digital communications channel equalization using radial basis function networks,'' IEEE Trans.
-Neural Networks, vol.
-4, pp.
-570--578, July 1993.
-\bibitem{c12} R. W. Lucky, ``Automatic equalization for digital communication,'' Bell Syst. Tech. J., vol. 44, no. 4, pp. 547--588, Apr. 1965.
-\bibitem{c13} S.
-P.
-Bingulac, ``On the compatibility of adaptive controllers (Published Conference Proceedings style),'' in Proc.
-4th Annu.
-Allerton Conf.
-Circuits and Systems Theory, New York, 1994, pp.
-8--16.
-\bibitem{c14} G. R. Faulhaber, ``Design of service systems with priority reservation,'' in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3--8.
-\bibitem{c15} W. D. Doyle, ``Magnetization reversal in films with biaxial anisotropy,'' in 1987 Proc. INTERMAG Conf., pp. 2.2-1--2.2-6.
-\bibitem{c16} G.
-W.
-Juette and L.
-E.
-Zeffanella, ``Radio noise currents n short sections on bundle conductors (Presented Conference Paper style),'' presented at the IEEE Summer power Meeting, Dallas, TX, June 22--27, 1990, Paper 90 SM 690-0 PWRS.
-\bibitem{c17} J. G. Kreifeldt, ``An analysis of surface-detected EMG as an amplitude-modulated noise,'' presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
-\bibitem{c18} J. Williams, ``Narrow-band analyzer (Thesis or Dissertation style),'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
-\bibitem{c19} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
-\bibitem{c20} J. P. Wilkinson, ``Nonlinear resonant circuit devices (Patent style),'' U.S. Patent 3 624 12, July 16, 1990.
+\bibitem{c1} Kaggle, "Grupo Bimbo Inventory Demand," Kaggle, 2016. [Online]. Available: \url{https://www.kaggle.com/competitions/grupo-bimbo-inventory-demand/overview}. [Accessed: 15-Jul-2024].
+
+\bibitem{c2} INEGI, "API del Banco de Indicadores," INEGI, 2024. [Online]. Available: \url{https://www.inegi.org.mx/servicios/api_indicadores.html#idMetodoIndicadoresInegi}. [Accessed: 15-Jul-2024].
 

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Paper and Report 90 percent

@@
 \subsection{Data Exploration}
+
+Initial data exploration involved understanding the structure and summary statistics of the dataset. Key columns include:
+
+\begin{itemize}
+    \item Week (Semana)
+    \item Sales Depot ID (Agencia\_ID)
+    \item Sales Channel ID (Canal\_ID)
+    \item Route ID (Ruta\_SAK)
+    \item Client ID (Cliente\_ID)
+    \item Client Name (NombreCliente)
+    \item Product ID (Producto\_ID)
+    \item Product Name (NombreProducto)
+    \item Sales Units This Week (Venta\_uni\_hoy)
+    \item Sales This Week in Pesos (Venta\_hoy)
+    \item Returns Units Next Week (Dev\_uni\_proxima)
+    \item Returns Next Week in Pesos (Dev\_proxima)
+    \item Adjusted Demand (Demanda\_uni\_equil)
+\end{itemize}
+
+Exploratory data analysis (EDA) was conducted to identify patterns, trends, and anomalies within the data.
+
 To understand the structure and characteristics of our dataset, we employed various graphical representations and utilized the YData Profile Report.
@@
 \section{Data Preprocessing}
-Invención de diodos emisores de luz azul que han permitido el desarrollo de fuentes de luz blanca y brillante de bajo consumo.\\\\
-1) Su invención ha revolucionado la iluminación de las dos últimas décadas al permitir generar una luz blanca, brillante y barata.\\
-2) Permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética.
+Data preprocessing is a critical step to ensure data quality and prepare it for modeling.
+\begin{itemize}
+    \item Data Cleaning: Missing values were handled, and duplicate records were removed. Outliers were identified and treated appropriately.
+    \item Data Integration: The external economic indicators (bi-weekly inflation and consumer confidence index) were integrated with the primary dataset based on the corresponding time periods.
+    \item Data Transformation: Features were transformed to appropriate data types to facilitate smooth pipeline operations.
+\end{itemize}
 
 \section{Feature Engineering}
-Los científicos japoneses Isamu Akasaki, Hiroshi Amano y Shuji Nakamura han conseguido el premio Nobel de Física 2014 por haber inventado el led azul, una nueva fuente de luz eficiente, duradera y amigable con el medioambiente.
-Su invento permitió crear lámparas led blancas, que emiten una luz brillante, son de larga duración y alta eficiencia energética.
-Constantemente están mejorando, con mayores flujos luminosos (medidos en lúmenes) por unidad de energía eléctrica de entrada (medido en vatios).
-El registro más reciente es poco más de 300 lm/ W, en comparación con los 16 de las bombillas regulares y los cerca de 70 de las lámparas fluorescentes.
+Feature engineering involved creating new variables to capture additional information and improve model performance.
+\begin{itemize}
+    \item Temporal Features: Lagged variables were created to capture temporal dependencies in sales and demand.
+    \item Economic Indicators: The bi-weekly inflation rate and consumer confidence index were added as features to capture the impact of economic conditions on product demand.
+    \item Categorical Encoding: Categorical variables were converted to numerical format using one-hot encoding or label encoding.
+\end{itemize}
 
 \section{Model Selection}
-Cuando Akasaki, Amano y Nakamura produjeron haces brillantes de luz azul en semiconductores a principio de la década de 1990, desencadenaron una transformación fundamental en la tecnología de iluminación.
-Los diodos verdes y rojos ya se conocían desde hacía tiempo, pero sin el componte azul, las lámparas blancas no se podían crear.
-La invención del led azul tiene solo 20 años, pero ya ha contribuido a crear luz blanca de una forma nueva beneficiándonos a todos.
+
+Two machine learning models were selected for this study: XGBoost and Random Forest.
+\begin{itemize}
+    \item XGBoost: A gradient boosting framework known for its high performance and ability to handle complex interactions.
+    \item Random Forest: An ensemble learning method that constructs multiple decision trees for improved robustness.
+\end{itemize}
 
 \section{Model Training}
-El premio nobel otorgado a los autores mencionados anteriormente ha sido para dar reconocimiento a la gran labor que ellos hicieron por la creación de un nuevo invento de bajo consumo.
-La invención del led azul tiene solo 20 años, pero ya ha contribuido a crear luz blanca de una forma nueva beneficiándonos a todos.
+The selected models were trained on the processed dataset.
+
+\begin{itemize}
+    \item $XGBoost$ Training: The XGBoost model was trained with parameters such as $n\_estimators=100$, $max\_depth=8$, $learning\_rate=0.1$, $subsample=0.8$, $colsample\_bytree=0.8$, and $random\_state=42$.
+    \item $Random$ $Forest$ Training: The Random Forest model was trained with parameters including $n\_estimators=100$, $max\_depth=...$
+\end{itemize}
 
 \section{Model Evaluation}
-ecuadoruniversitario.com  (2014).
-Quito – Ecuador.
-Isamu Akasaki, Hiroshi Amano y Shuji Nakamura reciben el Premio Nobel de Física 2014.
-Recuperado de: http://ecuadoruniversitario.com/ciencia-y-tecnologia/isamu-akasaki-hiroshi-amano-y-shuji-nakamura-reciben-el-premio-nobel-de-fisica-2014/
+Model performance was evaluated using root mean squared error (RMSE) as the primary metric.
+Additional metrics such as precision, recall, and F1-score were computed to provide a comprehensive evaluation.
+\begin{itemize}
+    \item XGBoost Performance: The XGBoost model achieved an RMSE of X, demonstrating its superior predictive accuracy.
+    \item Random Forest Performance: The Random Forest model had an RMSE of Y, indicating its relative performance compared to XGBoost.
+\end{itemize}
+
+\section{Business Questions}
+The study aimed to address several business questions related to inventory management and demand forecasting:
+\begin{itemize}
+    \item How can accurate demand forecasting improve inventory management?
+    \begin{itemize}
+        \item By predicting adjusted demand, Grupo Bimbo can optimize stock levels, reduce waste, and improve resource allocation.
+    \end{itemize}
+    \item What is the impact of economic indicators on product demand?
+    \begin{itemize}
+        \item The inclusion of bi-weekly inflation and consumer confidence index data provides insights into how economic conditions influence demand, allowing for more informed decision-making.
+    \end{itemize}
+\end{itemize}
 
 \section{Conclusions}
-ecuadoruniversitario.com  (2014).
-Quito – Ecuador.
-Isamu Akasaki, Hiroshi Amano y Shuji Nakamura reciben el Premio Nobel de Física 2014.
-Recuperado de: http://ecuadoruniversitario.com/ciencia-y-tecnologia/isamu-akasaki-hiroshi-amano-y-shuji-nakamura-reciben-el-premio-nobel-de-fisica-2014/
-
-SINC.
-(2014).
-Madrid – España.
-Premio Nobel de Física 2014 para los creadores del led azul.
-Recuperado de: https://www.agenciasinc.es/Noticias/Premio-Nobel-de-Fisica-2014-para-los-creadores-del-led-azul
+This study demonstrates the effectiveness of machine learning models in forecasting product demand for Grupo Bimbo.
+The XGBoost model outperformed the Random Forest model, offering more accurate predictions.
+Integrating external economic indicators enhanced the model's accuracy.
+These findings can help improve inventory management, reduce waste, and optimize resource allocation.
+Future work could explore additional features and real-time model implementation for continuous insights.
 

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Heatmap Correlation
Business Questions

@@
     \item Categorical Encoding: Categorical variables were converted to numerical format using one-hot encoding or label encoding.
+
+\begin{figure}[H] 
+    \begin{center}
+    \centering
+    \includegraphics[width=0.9\textwidth]{images/output.png}
+    \caption{Heatmap correlation of the features}
+    \end{center}
+\end{figure}
+
 \end{itemize}
@@
 \begin{itemize}
-    \item How can accurate demand forecasting improve inventory management?
-    \begin{itemize}
-        \item By predicting adjusted demand, Grupo Bimbo can optimize stock levels, reduce waste, and improve resource allocation.
-    \end{itemize}
-    \item What is the impact of economic indicators on product demand?
-    \begin{itemize}
-        \item The inclusion of bi-weekly inflation and consumer confidence index data provides insights into how economic conditions influence demand, allowing for more informed decision-making.
-    \end{itemize}
+    \item What are our best and worst customers?
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.9\textwidth]{images/quest1.png}
+        \caption{Business Question 1}
+        \end{center}
+    \end{figure}
+
+    \item What is the relationship between sales growth rates (1 and 2) and adjusted demand?
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.9\textwidth]{images/quest2.png}
+        \caption{Business Question 2}
+        \end{center}
+    \end{figure}
+
+    \item How are our sales going against the returns, and our adjusted demand?
+
+    % \begin{figure}[H] 
+    %     \begin{center}
+    %     \centering
+    %     \includegraphics[width=0.9\textwidth]{images/quest2.png}
+    %     \caption{Business Question 3}
+    %     \end{center}
+    % \end{figure}
+
+    \item What are our most used routes?
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.9\textwidth]{images/quest4.png}
+        \caption{Business Question 3}
+        \end{center}
+    \end{figure}
+
 \end{itemize}

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Models

@@
 \begin{itemize}
-    \item $XGBoost$ Training: The XGBoost model was trained with parameters such as $n\_estimators=100$, $max\_depth=8$, $learning\_rate=0.1$, $subsample=0.8$, $colsample\_bytree=0.8$, and $random\_state=42$.
-    \item $Random$ $Forest$ Training: The Random Forest model was trained with parameters including $n\_estimators=100$, $max\_depth=...$
+    \item $XGBoost$ Training: The XGBoost model was trained with parameters such as $n\_estimators=200$, $max\_depth=8$, $learning\_rate=0.2$, $subsample=0.9$, $colsample\_bytree=0.8$, $n\_jobs=-1$, and $random\_state=42$.
+    \item $Random$ $Forest$ Training: The Random Forest model was trained with parameters including $n\_estimators=110$, $min\_samples\_split=10$, $min\_samples\_leaf=5$, $n\_jobs=-1$, and $random\_state=42$.
 \end{itemize}

### 2024-07-15 src/data-science-project/data_science_project/docs/paper/paper.tex
Models
Documents 95 percent

@@
 \usepackage[T1]{fontenc}
+\usepackage{float} 
+\usepackage{graphicx}
 \usepackage{url}
@@
         \begin{itemize}
-                \item $\textbf{Parameters}$: $n\_estimators=100$, \\$max\_depth=8$, $learning\_rate=0.1$, $subsample=0.8$, $colsample\_bytree=0.8$, $random\_state=42$.
+                \item $\textbf{Parameters}$: $n\_estimators=200$, $max\_depth=8$, $learning\_rate=0.2$, $subsample=0.9$, $colsample\_bytree=0.8$, $n\_jobs=-1$, and $random\_state=42$.
         \end{itemize}
@@
         \begin{itemize}
-                \item $\textbf{Parameters}$: $n\_estimators=100$, \\$max\_depth=10$, $random\_state=42$.
+                \item $\textbf{Parameters}$: $n\_estimators=110$, $min\_samples\_split=10$, $min\_samples\_leaf=5$, $n\_jobs=-1$, and $random\_state=42$.
         \end{itemize}
@@
 The performance of the XGBoost and Random Forest models was evaluated based on the RMSE.
-The XGBoost model achieved an RMSE of X, indicating better predictive accuracy compared to the Random Forest model, which had an RMSE of Y.
-The superior performance of XGBoost can be attributed to its ability to handle complex interactions between features and its robustness to overfitting.
+The Random Forest model achieved an RMSE of X, indicating better predictive accuracy compared to the XGBoost model, which had an RMSE of Y.
+The superior performance of Random Forest can be attributed to its ability to handle high-dimensional data and its robustness to overfitting.
 The inclusion of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, further enhanced the model's predictive capabilities.
-Detailed performance metrics, including precision, recall, and F1-score, were also computed to provide a comprehensive evaluation of the models.
+
+\begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.9\textwidth]{images/comparison.jpg}
+        \caption{Actual vs Predict Adjusted Demand}
+        \end{center}
+\end{figure}
+
+\begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.9\textwidth]{images/comparisonxg.jpg}
+        \caption{Actual vs Predict Adjusted Demand}
+        \end{center}
+\end{figure}
 

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Documents 95 percent
Docs 96 percent
Conclusion Documents

@@
 \begin{itemize}
-    \item XGBoost Performance: The XGBoost model achieved an RMSE of X, demonstrating its superior predictive accuracy.
-    \item Random Forest Performance: The Random Forest model had an RMSE of Y, indicating its relative performance compared to XGBoost.
+    \item XGBoost Performance:
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.8\textwidth]{images/comparisonxg.jpg}
+        \caption{Heatmap correlation of the features}
+        \end{center}
+    \end{figure}
+
+    \item Random Forest Performance:
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.8\textwidth]{images/comparison.jpg}
+        \caption{Actual vs Predict Adjusted Demand}
+        \end{center}
+    \end{figure}
+
 \end{itemize}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{images/quest1.png}
+        \includegraphics[width=0.8\textwidth]{images/quest1.png}
         \caption{Business Question 1}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{images/quest2.png}
+        \includegraphics[width=0.8\textwidth]{images/quest2.png}
         \caption{Business Question 2}
@@
     %     \centering
-    %     \includegraphics[width=0.9\textwidth]{images/quest2.png}
+    %     \includegraphics[width=0.7\textwidth]{images/quest2.png}
     %     \caption{Business Question 3}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{images/quest4.png}
+        \includegraphics[width=0.8\textwidth]{images/quest4.png}
         \caption{Business Question 3}
@@
 \section{Conclusions}
-This study demonstrates the effectiveness of machine learning models in forecasting product demand for Grupo Bimbo.
-The XGBoost model outperformed the Random Forest model, offering more accurate predictions.
-Integrating external economic indicators enhanced the model's accuracy.
-These findings can help improve inventory management, reduce waste, and optimize resource allocation.
-Future work could explore additional features and real-time model implementation for continuous insights.
-
+This report demonstrates the application of machine learning models in forecasting product demand for Grupo Bimbo.
+The Random Forest model outperformed the XGBoost model, providing more accurate predictions of adjusted demand.
+The integration of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, significantly enhanced the model's accuracy.
+These findings highlight the potential of using advanced machine learning techniques to improve inventory management, reduce waste, and optimize resource allocation for Grupo Bimbo.
+Future work could involve incorporating additional features, such as macroeconomic indicators and weather data, to further enhance prediction accuracy.
 \end{document}

### 2024-07-15 src/data-science-project/data_science_project/docs/paper/paper.tex
Docs 96 percent
Conclusion Documents
Images Documents

@@
 \section{RESULTS}
-The performance of the XGBoost and Random Forest models was evaluated based on the RMSE.
+The performance of the XGBoost and Random Forest models were evaluated based on the RMSE.
 The Random Forest model achieved an RMSE of X, indicating better predictive accuracy compared to the XGBoost model, which had an RMSE of Y.
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{images/comparison.jpg}
+        \includegraphics[width=0.5\textwidth]{images/comparison.jpg}
         \caption{Actual vs Predict Adjusted Demand}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{images/comparisonxg.jpg}
+        \includegraphics[width=0.5\textwidth]{images/comparisonxg.jpg}
         \caption{Actual vs Predict Adjusted Demand}
@@
 This study demonstrates the potential of machine learning models in forecasting product demand for Grupo Bimbo.
-The XGBoost model outperformed the Random Forest model, offering more accurate predictions of adjusted demand.
+The Random Forest model outperformed the XGBoost model, offering more accurate predictions of adjusted demand.
 The integration of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, proved beneficial in enhancing the model's accuracy.

### 2024-07-15 src/data-science-project/data_science_project/docs/paper/paper.tex
Paper 100 percent

@@
 \subsection{Data Preprocessing}
-The preprocessing steps included:
+The preprocessing steps undertaken in this study involved several key processes to ensure the data was clean, consistent, and suitable for model training. Below are the detailed steps followed:
 \begin{itemize}                
-        \item \textbf{Data Cleaning}: Handling missing values and removing duplicates.
-        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
-        \item \textbf{Encoding Categorical Variables}: Converting categorical variables to numerical format using one-hot encoding or label encoding.
-        \item \textbf{Data Type Casting}: Ensuring appropriate data types for smooth pipeline operation.
+        \item \textbf{Data Cleaning}: 
+        \begin{itemize}
+                \item Handling Missing Values: Missing values in the dataset were identified and appropriately handled.
+For numerical columns, missing values were filled with the median of the column, while for categorical columns, the mode was used.
+        \end{itemize}
+        \item Outliers Removal: Outliers were detected using z-score and IQR methods and were removed or capped to prevent them from skewing the model results.
+
+        \item Data Transformation:
+        \begin{itemize}
+                \item Normalization and Scaling: Numerical features were normalized and scaled to ensure all features contribute equally to the model.
+StandardScaler from sklearn was used to transform features to have zero mean and unit variance.
+                \item Encoding Categorical Variables: Categorical variables were converted into numerical values using one-hot encoding for nominal variables and label encoding for ordinal variables.
         \end{itemize}
 
+        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
+        \begin{itemize}
+                \item Temporal Features: New temporal features such as the day of the week, month, and lag features for past sales data were created to capture temporal dependencies and seasonality in the data.
+                \item Interaction Features: Interaction features between different variables were created to capture complex relationships within the data.
+                \item External Economic Indicators: The bi-weekly inflation rate and consumer confidence index were merged with the primary dataset to capture the economic conditions impacting product demand.
+        \end{itemize}
+\end{itemize}
+
+\begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.5\textwidth]{images/output.png}
+        \caption{Heatmap Feature Information}
+        \end{center}
+\end{figure}
+
 \subsection{Modeling}
-Two machine learning models were employed:
+Two machine learning models were chosen for this study based on their ability to handle large datasets and complex relationships: XGBoost and Random Forest.
 \begin{itemize}
-        \item XGBoost: A gradient boosting framework optimized for performance.
+        \item XGBoost: XGBoost (Extreme Gradient Boosting) is an efficient and scalable implementation of gradient boosting framework by Friedman et al.
+It provides parallel tree boosting that solves many data science problems in a fast and accurate way.
         \begin{itemize}
@@
         \end{itemize}
-        \item Random Forest: An ensemble learning method using multiple decision trees.
+        \item Random Forest is an ensemble learning method for classification, regression, and other tasks that operates by constructing a multitude of decision trees at training time.
         \begin{itemize}
@@
 
-\subsection{Data Preprocessing}
-The preprocessing steps included:
+\subsection{Evaluation}
+Model performance was evaluated using the root mean squared error (RMSE) as the primary metric.
+RMSE is a standard way to measure the error of a model in predicting quantitative data.
+Additionally, other metrics such as R-squared, Mean Absolute Error (MAE), and Mean Squared Error (MSE) were also considered for a comprehensive evaluation.
 \begin{itemize}
-        \item \textbf{Data Cleaning}: Handling missing values and removing duplicates.
-        \item \textbf{Feature Engineering}: Creating new features such as lagged variables to capture temporal dependencies and integrating external economic indicators.
-        \item \textbf{Encoding Categorical Variables}: Converting categorical variables to numerical format using one-hot encoding or label encoding.
-        \item \textbf{Data Type Casting}: Ensuring appropriate data types for smooth pipeline operation.
+        \item XGBoost Performance:
+
+        \begin{itemize}
+                \item RMSE: The RMSE for the XGBoost model was X.
+                \item Other Metrics:
+                \begin{itemize}
+                        \item R-squared: The model's R-squared value was Y.
+                        \item MAE: The Mean Absolute Error for the model was Z.
+                        \item MSE: The Mean Squared Error for the model was W.
+                \end{itemize}
         \end{itemize}
 
-\subsection{Evaluation}
-Model performance was assessed using the root mean squared error (RMSE) to measure prediction accuracy.
+        \item Random Forest Performance: is an ensemble learning method for classification, regression, and other tasks that operates by constructing a multitude of decision trees at training time.
+
+        \begin{itemize}
+                \item RMSE: The RMSE for the Random Forest model was A.
+                \item Other Metrics:
+                \begin{itemize}
+                        \item R-squared: The model's R-squared value was B.
+                        \item MAE: The Mean Absolute Error for the model was C.
+                        \item MSE: The Mean Squared Error for the model was D.
+                \end{itemize}
+        \end{itemize}
+\end{itemize}
 
@@
         \includegraphics[width=0.5\textwidth]{images/comparison.jpg}
-        \caption{Actual vs Predict Adjusted Demand}
+        \caption{Actual vs Predict Adjusted Demand RandomForest}
         \end{center}
@@
         \includegraphics[width=0.5\textwidth]{images/comparisonxg.jpg}
-        \caption{Actual vs Predict Adjusted Demand}
+        \caption{Actual vs Predict Adjusted Demand XGBoost}
         \end{center}

### 2024-07-16 src/data-science-project/data_science_project/docs/report/report.tex
Business questions

@@
 \begin{itemize}
-    \item What are our best and worst customers?
+    \item What are our best customers per week?
 
@@
         \centering
-        \includegraphics[width=0.8\textwidth]{images/quest1.png}
+        \includegraphics[width=0.8\textwidth]{images/question1.jpg}
         \caption{Business Question 1}
@@
 
-    \item What is the relationship between sales growth rates (1 and 2) and adjusted demand?
+    \item What are the sales that WAL MART TEPEYAC had during the weeks?
 
@@
         \centering
-        \includegraphics[width=0.8\textwidth]{images/quest2.png}
+        \includegraphics[width=0.8\textwidth]{images/question2.jpg}
         \caption{Business Question 2}
@@
 
-    \item How are our sales going against the returns, and our adjusted demand?
-
-    % \begin{figure}[H] 
-    %     \begin{center}
-    %     \centering
-    %     \includegraphics[width=0.7\textwidth]{images/quest2.png}
-    %     \caption{Business Question 3}
-    %     \end{center}
-    % \end{figure}
-
-    \item What are our most used routes?
+    \item How many sales and returns where done for each week?
 
@@
         \centering
-        \includegraphics[width=0.8\textwidth]{images/quest4.png}
+        \includegraphics[width=0.7\textwidth]{images/question3.jpg}
+        \caption{Business Question 3}
+        \end{center}
+    \end{figure}
+
+    \item What are the top 10 products with most sales?
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.8\textwidth]{images/question4.jpg}
         \caption{Business Question 3}

### 2024-07-16 src/data-science-project/data_science_project/docs/paper/paper.tex
Paper Features
Paper Evaluation 1.0

@@
 StandardScaler from sklearn was used to transform features to have zero mean and unit variance.
-                \item Encoding Categorical Variables: Categorical variables were converted into numerical values using one-hot encoding for nominal variables and label encoding for ordinal variables.
         \end{itemize}
@@
         \begin{itemize}
-                \item Temporal Features: New temporal features such as the day of the week, month, and lag features for past sales data were created to capture temporal dependencies and seasonality in the data.
+                \item Temporal Features: Change to week features to datetime format and put as index.
                 \item Interaction Features: Interaction features between different variables were created to capture complex relationships within the data.
+                \begin{itemize}
+                        \item \textbf{Sales\_Growth\_Rate\_1}: Demand for the same product in the previous week.
+                        \item \textbf{Sales\_Growth\_Rate\_2}: Demand for the same product two weeks ago.   
+                \end{itemize}
                 \item External Economic Indicators: The bi-weekly inflation rate and consumer confidence index were merged with the primary dataset to capture the economic conditions impacting product demand.

### 2024-07-16 src/data-science-project/data_science_project/docs/paper/paper.tex
Documents ready

@@
 \subsection{Evaluation}
-Model performance was evaluated using the root mean squared error (RMSE) as the primary metric.
-RMSE is a standard way to measure the error of a model in predicting quantitative data.
-Additionally, other metrics such as R-squared, Mean Absolute Error (MAE), and Mean Squared Error (MSE) were also considered for a comprehensive evaluation.
+In this section, we evaluate and compare the performance of two machine learning models, Random Forest and XGBoost, on the task of predicting adjusted demand.
+We use metrics such as Mean Squared Error (MSE) and R-squared (R²) to assess the models' performance.
 \begin{itemize}
+
+        \item Metrics Used:
+        \begin{itemize}
+                \item Mean Squared Error (MSE): Measures the average of the squares of the errors—that is, the average squared difference between the estimated values and the actual value.  
+                \item R-squared (R²): Indicates the proportion of the variance in the dependent variable that is predictable from the independent variables.
+        \end{itemize}
+
         \item XGBoost Performance:
@@
         \begin{itemize}
-                \item RMSE: The RMSE for the XGBoost model was X.
-                \item Other Metrics:
-                \begin{itemize}
-                        \item R-squared: The model's R-squared value was Y.
-                        \item MAE: The Mean Absolute Error for the model was Z.
-                        \item MSE: The Mean Squared Error for the model was W.
-                \end{itemize}
+                \item Mean Squared Error (MSE): 331.45
+                \item R² Score: 0.342
         \end{itemize}
 
-        \item Random Forest Performance: is an ensemble learning method for classification, regression, and other tasks that operates by constructing a multitude of decision trees at training time.
+        The XGBoost model shows a higher MSE of 331.45 and a lower R² score of 0.342 compared to the Random Forest model.
+This indicates that only 34.2\% of the variance in the adjusted demand can be explained by the XGBoost model.
+
+        \item Random Forest Performance:
 
         \begin{itemize}
-                \item RMSE: The RMSE for the Random Forest model was A.
-                \item Other Metrics:
-                \begin{itemize}
-                        \item R-squared: The model's R-squared value was B.
-                        \item MAE: The Mean Absolute Error for the model was C.
-                        \item MSE: The Mean Squared Error for the model was D.
+                \item Mean Squared Error (MSE): 293.95
+                \item R² Score: 0.416
         \end{itemize}
-        \end{itemize}
+
+        These results indicate that the Random Forest model has a moderate fit to the data, with an MSE of 293.95 and an R² score of 0.416, meaning approximately 41.6\% of the variance in the adjusted demand can be explained by the model.
+
 \end{itemize}

### 2024-07-16 src/data-science-project/data_science_project/docs/report/report.tex
Question n5
Documents ready

@@
 \section{Model Evaluation}
-Model performance was evaluated using root mean squared error (RMSE) as the primary metric.
-Additional metrics such as precision, recall, and F1-score were computed to provide a comprehensive evaluation.
+In this section, we evaluate and compare the performance of two machine learning models, Random Forest and XGBoost, on the task of predicting adjusted demand.
+We use metrics such as Mean Squared Error (MSE) and R-squared (R²) to assess the models' performance.
 \begin{itemize}
@@
         \includegraphics[width=0.8\textwidth]{images/question4.jpg}
-        \caption{Business Question 3}
+        \caption{Business Question 4}
+        \end{center}
+    \end{figure}
+
+    \item What are the states and towns where there have been more sales?
+
+    \begin{figure}[H] 
+        \begin{center}
+        \centering
+        \includegraphics[width=0.8\textwidth]{images/question5.jpg}
+        \caption{Business Question 5}
         \end{center}

### 2024-07-16 src/data-science-project/data_science_project/docs/paper/paper.tex
Orthography

@@
         \begin{itemize}
-                \item Normalization and Scaling: Numerical features were normalized and scaled to ensure all features contribute equally to the model.
-StandardScaler from sklearn was used to transform features to have zero mean and unit variance.
+                \item Change type data: The columns were optimized by changing the data type (for example, going from int64 to int8)
         \end{itemize}

### 2024-07-16 src/data-science-project/data_science_project/docs/report/report.tex
Orthography

@@
 \section{Feature Engineering}
-Feature engineering involved creating new variables to capture additional information and improve model performance.
+Feature engineering involved creating new variables to capture additional information and improve model performance; and all characteristics were chosen except for inflation.
 \begin{itemize}
@@
     \item Economic Indicators: The bi-weekly inflation rate and consumer confidence index were added as features to capture the impact of economic conditions on product demand.
-    \item Categorical Encoding: Categorical variables were converted to numerical format using one-hot encoding or label encoding.
 
